A Large-Scale Study of the Use of Eval in R

### 2020-08-28 inst/paper/main.tex
Fix R and the Design of Eval

The R Project is a tool for data analysis.  At its heart it is a {vectorized,
  dynamic, lazy, functional, object-oriented} programming language with an
unusual combination of features~\cite{ecoop12} designed to ease learning by
non-programmer and enable rapid development of statistical
methods~\cite{R96}.  The language was designed as a successor to
S~\cite{S88}.

@@

Most R data types are vectorized. Values are constructed by the \c{c(...)}
function, e.g., \c{c("hi","ho")} creates a vector of two strings.  R does
not differentiate scalars from vectors. To enable equational reasoning, R
copies values accessible through multiple variables when they are updated.
Values can be tagged by user-defined attributes. For instance, one can
attach the attribute \c{dim} to the value \c{x<-c(1,2,3,4)} with
\c{attr(x,"dim")<-c(2,2)}.  This causes arithmetic functions to treat \c x
as a 2x2 matrix. Another attribute is \c{class} which can be bound to a list
of names, e.g., \c{class(x)<-"human"}. This sets the class of \c{x} to
\c{human}, classes are used for object-oriented dispatch.  Every R
linguistic construct is desugared to a function call, even control flow
statements, assignments, and bracketing. Furthermore, all functions can be
redefined in user code. This makes R both flexible and challenging to
compile~\cite{dls19}.

>>>>

The R Project is a tool for data analysis.  At its heart it is a {vectorized,
  dynamic, lazy, functional, object-oriented} programming language with an
unusual combination of features~\cite{ecoop12} designed to ease learning by
non-programmers and enable rapid development of statistical
methods~\cite{R96}.  The language was designed as a successor to
S~\cite{S88}.

@@

Most R data types are vectorized. Values are constructed by the \c{c(...)}
function, e.g., \c{c("hi","ho")} creates a vector of two strings.  R does
not differentiate scalars from vectors. To enable equational reasoning, R
copies values accessible through multiple variables when they are updated.
Values can be tagged by user-defined attributes. For instance, one can
attach the attribute \c{dim} to the value \c{x<-c(1,2,3,4)} with
\c{attr(x,"dim")<-c(2,2)}.  This causes arithmetic functions to treat \c x
as a $2 \times 2$ matrix. Another attribute is \c{class} which can be bound to a list
of names, e.g., \c{class(x)<-"human"}. This sets the class of \c{x} to
\c{human}; classes are used for object-oriented dispatch.  Every R
linguistic construct is desugared to a function call, even control flow
statements, assignments, and bracketing. Furthermore, all functions can be
redefined in user code. This makes R both flexible and challenging to
compile~\cite{dls19}.
